---
title: "Gibbs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gibbs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

Function gibbs() can be found in R package Gibbs.
```{r setup}
library(Gibbs)
```
Function gibbs() can be used to do Gibbs sampling for simple linear regression with one parameter and one outcome. Gibbs sampling is one way (among many) to estimate a Bayesian model, to determine the best value of a parameter by generating a Markov chain of samples.

To use the gibbs() function, we need to get a set of independent values -- X, a set of dependent values corresponding to the independent values -- Y, and the number of the values -- n. Then we can fit in the gibbs() function using these values.

Aftering fitting the function, we get the following outputs:

GibbsSampleResult: This is a 30000*3 dataset with results of sampling for 30000 times. It includes 3 columns: Intercept -- the sampling intercept for Y~X, Slope -- the sampling slope for Y~X, sigma2 -- the sampling variance of residuals for Y~X.

GibbsSampleSummary: This is a 3*4 matrix with summaries of mean, standard deviation, 2.5% quantile, 97.5% quantile for Intercept, Slope and sigma2.

SD_Comparison: This is a 2*2 matrix of comparisons between sampling standard deviation and ordinary least square deviation for Intercept and Slope.

Plot of X (Variate) and Y (Response) with fitted line from OLS.

Histogram of the posterior slope -- which looks normally distributed.

Plot of X (Variate) and Y (Response), with the fitted line of Intercept mean and Slope mean from sampling.

Here is an example using a data set containing 67 rows of female babies named as 'Sophia', who were born after year 1950. We regress the log odds of a baby being named 'Sophia' (Y) onto the year (X). To improve convergence we standardize X first.
```{r}
library(Gibbs)
library(babynames)
X   <- scale(dat$year)
p   <- dat$prop
Y   <- log(p/(1-p))
n   <- length(X)

gibbs(X, Y, n)
```
From the out put we can see that the intercept for OLS is -7.188, the slope for OLS is 1.547. Also GibbsSampleSummary table, SD_Comparison table, plot of X and Y with fitted line from OLS, histogram of the posterior slope, plot of X and y with the fitted line of Intercept mean and Slope mean from sampling. We can also take a look at the first fews rows of the GibbsSampleResult.
```{r}
head(GibbsSampleResult)
```




